16s taxa stacked bar plot

### 2021-03-02 scripts/49_16s_stacked_barplot.Rmd
did this centroid thing anyway

dat$sampleid = factor(dat$sampleid,levels = div_order)

>>>>

###
# how about splitting the above dendrogram order into the low and higher diversity groups
div_med <- median(stb$simpson_reciprocal)
lower_samp <- stb %>% 
  filter(simpson_reciprocal <= div_med) %>% 
  pull(sampleid)
lower_samp_o <- sample_dendogram_order[sample_dendogram_order %in% lower_samp]
higher_samp_o <- sample_dendogram_order[!sample_dendogram_order %in% lower_samp]

dat$sampleid = factor(dat$sampleid,levels = c(lower_samp_o, higher_samp_o))
